\documentclass[a4paper,14pt]{article}
\usepackage[paperwidth=210mm,paperheight=297mm,centering,hmargin=2cm,vmargin=2.5cm]{geometry}
\usepackage{epsfig}
\usepackage{csquotes}
\usepackage{gensymb}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{appendix}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.4}
\usepackage{csquotes}
\usepackage{lineno}
\usepackage{authblk}
\usepackage[numbers,comma,super,sort&compress]{natbib}
\usepackage[colorlinks=true,linkcolor=blue]{hyperref}%
\makeatletter 
\renewcommand\@biblabel[1]{#1.} 
\makeatother
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=magenta,      
    urlcolor=darkblue,
}

\begin{document}
\noindent\textbf{\Large Swaminath Bharadwaj G.}\\
\rule{\textwidth}{1pt}\\\ \\
 \section*{\large Publications}
(h-index: 5, i10-index: 2, Total citations: 48)
\begin{enumerate}
\item
\enquote{Small-to-large length scale transition of TMAO interaction with hydrophobic solutes}
A. Folberth, \underline{S. Bharadwaj}, N. F. A. van der Vegt,
Physical Chemistry Chemical Physics 24 (4), 2080-2087, 2022. {\color{red} IF: 3.676} \\ 
\textbf{2022 PCCP HOT Articles}
\item
\enquote{Direct Calculation of Entropic Components in Cohesive Interaction Free Energies}
\underline{S. Bharadwaj}, S. Jabes B., N. F. A.  van der Vegt,
The Journal of Physical Chemistry B 125 (39), 11026-11035, 2021. {\color{red} IF: 2.991}\\
\textbf{Part of special issue \enquote{Dor Ben-Amotz Festschrift}}
\item
\enquote{An interplay of excluded-volume and polymer–(co) solvent attractive interactions regulates polymer collapse in mixed solvents}
\underline{S. Bharadwaj}, D. Nayar, C. Dalgicdir, N. F. A van der Vegt,
The Journal of Chemical Physics 154 (13), 134903, 2021. {\color{red}IF: 3.488}
\item
\textbf{Communication}: \enquote{A cosolvent surfactant mechanism affects polymer collapse in miscible good solvents}
\underline{S. Bharadwaj}, D. Nayar, C. Dalgicdir, N. F. A. van der Vegt,
Communications Chemistry 3 (1), 1-7, 2020. {\color{red}IF: 6.581}
\item
\enquote{Characterizing Polymer Hydration Shell Compressibilities with the Small-System Method}
M. Tripathy, \underline{S. Bharadwaj}$^{\ast}$, S. Jabes B., N. F. A. van der Vegt,
Nanomaterials 10 (8), 1460, 2020. IF: {\color{red}5.076} \\
$^{\ast}$Joint First Author\\
\textbf{Part of the special issue \enquote{Nanoscale Thermodynamics}}
\item
\enquote{Does preferential adsorption drive cononsolvency?}
S. Bharadwaj, N. F. A van der Vegt.
Macromolecules 52 (11), 4131-4138, 2019. {\color{red}IF: 5.985}
\item
\enquote{Kosmotropic effect leads to LCST decrease in thermoresponsive polymer solutions}
\underline{S. Bharadwaj}, P. B. Sunil Kumar, S. Komura, A. P. Deshpande,
The Journal of Chemical Physics 148 (8), 084903, 2018. {\color{red}IF: 3.488}
\item
\enquote{Spherically symmetric solvent is sufficient to explain the LCST mechanism in polymer solutions}
\underline{S. Bharadwaj}, P. B. Sunil Kumar, S. Komura, A. P Deshpande, Macromolecular Theory and Simulations 26 (2), 1600073, 2016. {\color{red} IF: 1.53}
\end{enumerate}
\subsection*{\normalsize Manuscripts under review}
\begin{enumerate}
\item
\enquote{Nonadditive ion effects on the coil-globule equilibrium of PNIPAM: A computer simulation study} Y. Zhao, \underline{S. Bharadwaj}$^{\ast}$, N. F. A. van der Vegt. Under review in Physical Chemistry Chemical Physics (2022).\\
$^{\ast}$Joint first author
\item
\enquote{Cononsolvency of thermoresponsive polymers: where we are now and where we are going} \underline{S. Bharadwaj}, B. J. Niebuur, K. Nothdurft, W. Richtering, N. F. A. van der Vegt, C. M. Papadakis. Under review in Soft Matter (2022).
\item
\enquote{Solvation Shell Thermodynamics of Extended Hydrophobic Solutes in
Mixed Solvents} M. Tripathy, \underline{S. Bharadwaj}$^{\ast}$, Nico F. A. van
der Vegt. Under review in The Journal of Chemical Physics (2022).\\
$^{\ast}$Joint first author
\end{enumerate}
\section*{Conferences}
\subsection*{\normalsize Oral Contributions}
\begin{enumerate}
\item
\enquote{Nonadditive ion effects on the solvation of thermoresponsive polymers
in aqueous solutions,}\\ \underline{Swaminath Bharadwaj} , Yani Zhao, Nico F. A.
van der Vegt. \textit{CompFlu}, Indian Institute of Technology Gandhinagar,
India, December 13-15, 2021.
\item
\enquote{A cosolvent surfactant mechanism affects polymer collapse in miscible
good solvents,} \\\underline{Swaminath Bharadwaj}. \textit{Osmolyte and Cosolvent
Effects in Stimuli-Responsive Soft Matter Systems}, Virtual conference
organized jointly by Technical University of Darmstadt and Technical University
of Munich, February 25-26, 2021.
\item
\enquote{On the mechanism of lower critical solution temperature and its
variation with co-solvents in thermoresponsive polymer solutions,}
\underline{Swaminath Bharadwaj}, P. B. Sunil Kumar, Shigeyuki Komura, Abhijit
P. Deshpande. \textit{CompFlu}, Indian Institute of Technology Madras,  Chennai,
India, December 18-20, 2017.
\item
\enquote{Effect of co-solvent on the LCST of thermoresponsive
polymers,} \underline{Swaminath Bharadwaj}, P. B. Sunil Kumar, Shigeyuki Komura,
Abhijit P. Deshpande. \textit{2nd International Conference on Soft Materials
(ICSM)}, Malaviya National Institute of Technology Jaipur, India, December
12-16, 2016. \textbf{Best Oral Presentation Award}
\end{enumerate}
\subsection*{\normalsize Poster Contributions}
\begin{enumerate}
\item
\enquote{Characterizing Polymer Hydration Shell Thermodynamics Using the Small
System Method,}\\  \underline{Swaminath Bharadwaj}, Nico van der Vegt.
\textit{Recent progress in the statistical mechanics of solutions through
Kirkwood-Buff integrals and related approaches}, Universit{\'e} de Bourgogne,
France, September 20-22, 2021
\item
\enquote{Coil-to-globule transitions in mixed solvents: A cosolvent surfactant
mechanism,} \underline{Swaminath Bharadwaj}, Nico van der Vegt. \textit{11th
Liquid Matter Conference}, Prague, July 19-23, 2021
\item
\enquote{A cosolvent surfactant mechanism affects polymer collapse in miscible
good solvents,}\\ \underline{Swaminath Bharadwaj}, Nico van der Vegt.
\textit{CompFlu}, Indian Institute of Technology Bombay, India, December 10-12,
2020.
\item
\enquote{On the mechanism of lower critical solution temperature and its
variation with co-solvents in thermoresponsive polymer
solutions,} \underline{Swaminath Bharadwaj}, P. B. Sunil Kumar, Shigeyuki
Komura, Abhijit P. Deshpande. \textit{10th Liquid Matter Conference}, Ljubljana,
Slovenia, July 17-21, 2017.
\item
\enquote{LCST behavior of thermoresponsive polymers in binary solvent
mixtures,} \underline{Swaminath Bharadwaj}, P. B. Sunil Kumar, Shigeyuki
Komura, Abhijit P. Deshpande. \textit{CompFlu}, Indian Institutes of Science
Education and Research, Pune, India, January 2-4, 2016.
\item
\enquote{Coil-to-globule transition in thermoresponsive polymer solutions,}
\underline{Swaminath Bharadwaj}, P. B. Sunil Kumar, Shigeyuki Komura, Abhijit
P. Deshpande. \textit{Physics of Structural and Dynamical Hierarchy in Soft
Matter}, Institute of Industrial Science, University of Tokyo, Japan, March
16-18, 2015.
\end{enumerate}
\end{document}

